Canonical rings of $\bq$-divisors on Minimal Rational Surfaces

### 2015-08-02 surfaces-write-up/surface-write-up.tex
agree with you guys for degrees at most...
fixed error in 4.4 proof

\noindent
where
\[
	\tau = \sigma
	+ \max \left( \max_{i\in \Te} \bigl(\ell_i \gcd(a_i, b_i) \bigr),
	\max_{\substack{i \in \Tp \\ j \in \Tm}} \bigl(\ell_{i, j}
	(\bida_i \bidb_j - \bida_j \bidb_i) \bigr) \right).
\]
\end{restatable}

@@

From this we can deduce that a set of extremal rays of $\Sigma$ are given as follows:
For $i \in \Te(D)$, define $e_i \in R_D$ in degree $d_i = \ell_i \gcd(a_i, b_i)$ by 
\begin{equation}\label{eqn:epsilon_i}
	e_i := d_i \epsilon_i %(-\alpha_1 d_i, \ldots, - \alpha_{i-1} d_i, \frac{d_i}{\bida_i + \bidb_i}\sum_{k \ne i}
	%\alpha_k (\bida_k + \bidb_k), - \alpha_{i+1} d_i, \ldots, - \alpha_n d_i)
\end{equation}

\noindent
For $i \in \Tp(D)$ and $j \in \Tm(D)$, with $i < j$, define $e_{i,j}\in R_D$ in degree $d_{i,j} = \ell_{i, j}(\bida_i \bidb_j - \bida_j \bidb_i)$ by
\begin{equation}\label{eqn:epsilon_i,j}
e_{i,j} := \frac{a_j\sum_{k\ne i,j} d_{i,j}\alpha_k b_k - b_j\sum_{k \ne i,j} d_{i,j} \alpha_k a_k}{a_ib_j - b_i a_j} \epsilon_i + \frac{a_i \sum_{k\ne i,j} d_{i,j} \alpha_k b_k - b_i\sum_{k\ne i,j} d_{i,j} \alpha_ka_k}{a_jb_i - b_j a_i} \epsilon_j
%	
%	(-\alpha_1 d_{i,j}, \ldots -\alpha_{i-1} d_{i,j}, \bidb_j \sum_{k \ne i,j} \alpha_k \bida_k - \bida_j \sum_{k \ne i, j}
%	\alpha_k \bidb_k, -\alpha_{i+1} d_{i,j}, \\
%	&\ldots -\alpha_{j-1} d_{i,j}, -\bidb_i \sum_{k \ne i, j} \alpha_k \bida_k + \bida_i \sum_{k \ne i, j}
%	\alpha_k \bidb_k, -\alpha_{j+1}d_{i,j}, \ldots, - \alpha_{n}d_{i,j}).
%	\end{split}
\end{equation}

@@

If $i\in \Tp$ choose $r_{i,j}\in \bq_{\ge 0}$ for all $j\in \Tm$ such that $\sum_{j\in \Tm} r_{i,j}\kappa_{i,j}' = 1$; similarly, if $i\in \Tm$ choose $r_{j,i}\in \bq_{\ge 0}$ for all $j\in \Tp$ such that $\sum_{j\in \Tm} r_{j,i}\kappa_{j,i}'' = 1$.
Define $E$ by
\begin{equation}\label{eqn:hirz-E-translation}
	E := \begin{cases}
	\frac{1}{\kappa_i} e_i  &  \mbox{ if }i\in \Te\\
	\sum_{j\in \Tm} r_{i,j} e_{i,j} & \mbox{ if } i\in \Tp\\
	\sum_{j\in \Tp} r_{j,i} e_{j,i} 	& \mbox{ if } i\in \Tm.
	\end{cases}
\end{equation}
Define
\begin{equation}\label{eqn:defn-lambda}
	\lambda = \sigma - E\in \Sigma.
 \end{equation}
Note that
\[
	\deg(E) \le \begin{cases}
	\ell_i \gcd(\bida_i, \bidb_i)	&\mbox{ if } i \in \Te \\
	\max_{j \in \Tm} \bigl(\ell_{i, j} (\bida_i \bidb_j - \bida_j \bidb_i)\bigr)
	&\mbox{ if } i \in \Tp \\
	\max_{j \in \Tp} \bigl(\ell_{j, i} (\bida_j \bidb_ i - \bida_i \bidb_j) \bigr)
	&\mbox{ if } i \in \Tm. \end{cases}
\]

Let $M_i$ be the set of monomials terms of $\beta_i$ (recall $\beta_i$ is a polynomial in $f_1, \ldots f_4$).  Let $\mu = \prod_{j=1}^4
{f_j}^{h_j}\in M_i$ and consider the lattice point (in the same degree $d$ as $\sigma$)
\[
	\sigma_\mu = (d, c_1 + h_1, \ldots, c_4+h_4, c_5, \ldots, c_n).
\]
Define 
\[
	E_\mu = \sigma_\mu - \lambda.
\]
A quick computation deduces that $E_\mu$ lies in $\Sigma$ (using the condition on the $r_{i,j}$'s and $r_{j,i}'s$) and has the same degree as $E$.

Let $F\in R_D$ be the monomial given by the lattice point $E$ and $F_\mu \in R_D$ be the monomial given by the lattice point $E_\mu$ for each $\mu \in M_i$.  
Then $F - \sum_{\mu \in M} F_\mu = 0$ is a relation %in degree
%\[
%	\deg(F) = \deg(E)
%\]
which divides $(z_i - \beta_i) \prod_{i = 1}^n y_i^{c_i}$. 
We can bound $\deg(F)$ (which equals $\deg(F_\mu)$ for all $\mu$) by
\[
	\deg(F) = \deg(E) \le \begin{cases}
	\ell_i \gcd(\bida_i, \bidb_i)	&\mbox{ if } i \in \Te \\
	\max_{j \in \Tm} \bigl(\ell_{i, j} (\bida_i \bidb_j - \bida_j \bidb_i)\bigr)
	&\mbox{ if } i \in \Tp \\
	\max_{j \in \Tp} \bigl(\ell_{j, i} (\bida_j \bidb_ i - \bida_i \bidb_j) \bigr)
	&\mbox{ if } i \in \Tm. \end{cases}
	\]

>>>>

\noindent
where
\[
	\tau = \rho
	+ \max \left( \max_{i\in \Te} \bigl(\ell_i \gcd(a_i, b_i) \bigr),
	\max_{\substack{i \in \Tp \\ j \in \Tm}} \bigl(\ell_{i, j}
	(\bida_i \bidb_j - \bida_j \bidb_i) \bigr) \right).
\]
\end{restatable}

@@

From this we can deduce that a set of extremal rays of $\Sigma$ are given as follows:
For $i \in \Te(D)$, define $e_i \in R_D$ in degree 
\[
	d_i = \ell_i \gcd(a_i, b_i)
\]
by 
\begin{equation}\label{eqn:epsilon_i}
	e_i := d_i \epsilon_i %(-\alpha_1 d_i, \ldots, - \alpha_{i-1} d_i, \frac{d_i}{\bida_i + \bidb_i}\sum_{k \ne i}
	%\alpha_k (\bida_k + \bidb_k), - \alpha_{i+1} d_i, \ldots, - \alpha_n d_i)
\end{equation}

\noindent
For $i \in \Tp(D)$ and $j \in \Tm(D)$, with $i < j$, define $e_{i,j}\in R_D$ in degree 
\[
	d_{i,j} = \ell_{i, j}(\bida_i \bidb_j - \bida_j \bidb_i)
\]
by
\begin{equation}\label{eqn:epsilon_i,j}
e_{i,j} := \frac{a_j\sum_{k\ne i,j} d_{i,j}\alpha_k b_k - b_j\sum_{k \ne i,j} d_{i,j} \alpha_k a_k}{a_ib_j - b_i a_j} \epsilon_i + \frac{a_i \sum_{k\ne i,j} d_{i,j} \alpha_k b_k - b_i\sum_{k\ne i,j} d_{i,j} \alpha_ka_k}{a_jb_i - b_j a_i} \epsilon_j
%	
%	(-\alpha_1 d_{i,j}, \ldots -\alpha_{i-1} d_{i,j}, \bidb_j \sum_{k \ne i,j} \alpha_k \bida_k - \bida_j \sum_{k \ne i, j}
%	\alpha_k \bidb_k, -\alpha_{i+1} d_{i,j}, \\
%	&\ldots -\alpha_{j-1} d_{i,j}, -\bidb_i \sum_{k \ne i, j} \alpha_k \bida_k + \bida_i \sum_{k \ne i, j}
%	\alpha_k \bidb_k, -\alpha_{j+1}d_{i,j}, \ldots, - \alpha_{n}d_{i,j}).
%	\end{split}
\end{equation}

@@

If $i\in \Te$ define $r_i := \frac{1}{\kappa_i}$.  If $i\in \Tp$ choose $r_{i,j}\in \bq_{\ge 0}$ for all $j\in \Tm$ such that $\sum_{j\in \Tm} r_{i,j}\kappa_{i,j}' = 1$; similarly, if $i\in \Tm$ choose $r_{j,i}\in \bq_{\ge 0}$ for all $j\in \Tp$ such that $\sum_{j\in \Tm} r_{j,i}\kappa_{j,i}'' = 1$.  For $j,k\ne i$, define all $r_j$ and $r_{j,k}$'s to be 0.
Define $E$ by
\begin{equation}\label{eqn:hirz-E-translation}
	E := \sum_{j\in \Te} (s_j - \lfloor s_j - r_j\rfloor) e_j + \sum_{\substack{j\in \Tp \\ k\in \Tm}} (s_{j,k} - \lfloor s_{j,k} - r_{j,k}\rfloor)e_{j,k}.
\end{equation}
Define
\begin{equation}\label{eqn:defn-lambda}
	\lambda := \sigma - E = \sum_{j\in \Te} (\lfloor s_j - r_j\rfloor) e_j + \sum_{\substack{j\in \Tp \\ k\in \Tm}} ( \lfloor s_{j,k} - r_{j,k}\rfloor)e_{j,k}\in \Sigma.
 \end{equation}
Note that
\[
	\deg(E) \le \rho + \begin{cases}
	\ell_i \gcd(\bida_i, \bidb_i)	&\mbox{ if } i \in \Te \\
	\max_{j \in \Tm} \bigl(\ell_{i, j} (\bida_i \bidb_j - \bida_j \bidb_i)\bigr)
	&\mbox{ if } i \in \Tp \\
	\max_{j \in \Tp} \bigl(\ell_{j, i} (\bida_j \bidb_ i - \bida_i \bidb_j) \bigr)
	&\mbox{ if } i \in \Tm. \end{cases}
\]
where $\rho$ is as in Equation \ref{eqn:def-sigma}.

Let $M_i$ be the set of monomials terms of $\beta_i$ (recall $\beta_i$ is a polynomial in $f_1, \ldots f_4$).  Let $\mu = \prod_{j=1}^4
{f_j}^{h_j}\in M_i$ and consider the lattice point (in the same degree $d$ as $\sigma$)
\[
	\sigma_\mu = (d, c_1 + h_1, \ldots, c_4+h_4, c_5, \ldots, c_n).
\]
Define 
\[
	E_\mu = \sigma_\mu - \lambda.
\]
A quick computation deduces that $E_\mu$ lies in $\Sigma$ (using the condition on the $r_{i,j}$'s and $r_{j,i}s$) and has the same degree as $E$.

Let $F\in R_D$ be the monomial given by the lattice point $E$ and $F_\mu \in R_D$ be the monomial given by the lattice point $E_\mu$ for each $\mu \in M_i$.  
Then $F - \sum_{\mu \in M_i} F_\mu = 0$ is a relation %in degree
%\[
%	\deg(F) = \deg(E)
%\]
which divides $(z_i - \beta_i) \prod_{j = 1}^n z_j^{c_j}$. 
We can bound $\deg(F)$ (which equals $\deg(F_\mu)$ for all $\mu$) by
\[
	\deg(F) = \deg(E) \le \rho + \begin{cases}
	\ell_i \gcd(\bida_i, \bidb_i)	&\mbox{ if } i \in \Te \\
	\max_{j \in \Tm} \bigl(\ell_{i, j} (\bida_i \bidb_j - \bida_j \bidb_i)\bigr)
	&\mbox{ if } i \in \Tp \\
	\max_{j \in \Tp} \bigl(\ell_{j, i} (\bida_j \bidb_ i - \bida_i \bidb_j) \bigr)
	&\mbox{ if } i \in \Tm. \end{cases}
	\]
